Forecasting the black Sigatoka development rate: A comparison of machine learning techniques

### 2015-11-29 Paper Sigatoka - 2015.tex
2015-11-28 Algunos cambios mas la inclusion de elastic-net

In Costa Rica for the control of black Sigatoka is necessary the application of chemical fungicides. Depending of the zone of production and the weather conditions 45 – 55 cycles/year of fungicides is needed to keep this disease under control and to produce fruit with quality for exportation. This represent a cost per hectare per year ranged between \$1600 USD and \$2000 USD, about 0,64 - 0.80 cents of the cost of production of a box of 18.14 kilograms. Overall, this represents 10\% to 12\% of the total production cost.

@@

In this work, we compare four machine learning techniques (support vector
regression (SVR), echo state networks (ESN), ridge regression and
ordinary least squares linear regression) to predict the development rate of the black Sigatoka disease.

@@

\begin{equation} 
\begin{aligned}
& \underset{}{\text{miimize}}
& & J(w,\xi_i , \xi_i^* ) = \frac{1}{2}   \Bigr| \Bigr| w \Bigr| \Bigr|^2 + C \sum_{i=1}^{n} (\xi_i , \xi_i^* )    \\
& \text{subject to}
& & \begin{array}{lcl} 
y_i - w^T \phi (s) - b  \leq \epsilon + \xi_i   \\
w^T \phi (s) + b - y_i \leq \epsilon + \xi_i^* & i= 1,2,...,n \\
\xi_i , \xi_i^* \geq 0  \\
\end{array}
\end{aligned}
\end{equation}  
where $C$ denotes the penalty parameter between empirical and generalization errors, and  $\xi_i , \xi_i^*$ are slack variables. \figurename
$.$\ref{figura2} shows this situation.

@@

\subsubsection{Ridge regression}
The ridge regression addresses some of the problems of ordinary least squares regression by imposing a penalty on the size of the coefficients. The ridge coefficients minimize a penalized residual sum of squares  \citep{scikitlearn2011}:
$$\min_{w} { \Bigr| \Bigr| Xw - y \Bigr| \Bigr|_2^2  + \alpha \Bigr| \Bigr| w \Bigr| \Bigr|_2^2 } $$
Here, $\alpha \ \textgreater \  0$ is a complexity parameter that controls the amount of shrinkage: the larger the value of $\alpha$, the greater the amount of shrinkage and thus the coefficients become more robust to collinearity.

@@

Although there are many types of indicators to assess the quality of the prediction, we selected the root mean square error $(RMSE)$ and the determination coefficient $(R^2)$.

Given $n$ records, let be $y$ the actual value of the series, $\hat{y}$ the predicted value and $\acute{y}$ the mean of the observed data.
$$RMSE = \sqrt{ \sum_{i=1}^{n} \frac{{(y-\hat{y})}^2}{n} }$$

@@

\begin{itemize}
\item 	Patterns: n by m, where n from 1 to 8 and m from 1 to 3.

\item Methods: support vector regression with the kernels functions: linear, RBF (Gaussian) and sigmoid; echo state networks; ordinary least squares linear regression and ridge regression.

>>>>

In Costa Rica for the control of black Sigatoka is necessary the application of chemical fungicides. Depending of the zone of production and the weather conditions 45 - 55 cycles/year of fungicides is needed to keep this disease under control and to produce fruit with quality for exportation. This represent a cost per hectare per year ranged between \$1600 USD and \$2000 USD, about 0,64 - 0.80 cents of the cost of production of a box of 18.14 kilograms. Overall, this represents 10\% to 12\% of the total production cost.

@@

In this work, we compare five machine learning techniques (support vector
regression (SVR), echo state networks (ESN), ridge regression, elastic-net regression and
ordinary least squares linear regression) to predict the development rate of the black Sigatoka disease.

@@

\begin{equation} 
\begin{aligned}
& \underset{}{\text{minimize}}
& & J(w,\xi_i , \xi_i^* ) = \frac{1}{2}   \Bigr| \Bigr| w \Bigr| \Bigr|^2 + C \sum_{i=1}^{n} (\xi_i , \xi_i^* )    \\
& \text{subject to}
& & \begin{array}{lcl} 
y_i - w^T \phi (s) - b  \leq \epsilon + \xi_i   \\
w^T \phi (s) + b - y_i \leq \epsilon + \xi_i^* & i= 1,2,...,n \\
\xi_i , \xi_i^* \geq 0  \\
\end{array}
\end{aligned}
\end{equation}  
where $C$ denotes the penalty parameter between empirical and generalization errors, and  $\xi_i , \xi_i^*$ are slack variables. \figurename
$.$\ref{figura2} shows this situation.

@@

\subsubsection{Ridge regression}
The ridge regression addresses some of the problems of ordinary least squares regression by imposing a penalty on the size of the coefficients. The ridge coefficients minimize a penalized residual sum of squares  \citep{scikitlearn2011}:

$$\min_{w} { \Bigr| \Bigr| Xw - y \Bigr| \Bigr|_2^2  + \alpha \Bigr| \Bigr| w \Bigr| \Bigr|_2^2 } $$

Here, $\alpha \ \textgreater \  0$ is a complexity parameter that controls the amount of shrinkage: the larger the value of $\alpha$, the greater the amount of shrinkage and thus the coefficients become more robust to collinearity.

\subsubsection{Elastic-Net regression}
Elastic-Net is a linear regression model trained with $L1$ and $L2$ prior as regularizer. This combination allows for learning a sparse model where few of the weights are non-zero like Lasso, while still maintaining the regularization properties of Ridge  \citep{scikitlearn2011}. The convex combination of $L1$ and $L2$ is controled by using the $l1_ratio$ parameter.

Elastic-Net is useful when there are multiple features which are correlated with one another. Lasso is likely to pick one of these at random, while elastic-net is likely to pick both.
A practical advantage of trading-off between Lasso and Ridge is it allows Elastic-Net to inherit some of Ridge’s stability under rotation. The objective function to minimize is \citep{scikitlearn2011}:

$$\min_{w} { \frac{1}{2n_{samples}} \Bigr| \Bigr| Xw - y \Bigr| \Bigr|_2^2  + \alpha \rho \Bigr| \Bigr| w \Bigr| \Bigr|_1 + \frac{\alpha (1- \rho)}{2} \Bigr| \Bigr| w \Bigr| \Bigr|_2^2 } $$

@@

Although there are many types of indicators to assess the quality of the prediction, we selected the determination coefficient $(R^2)$.

Given $n$ records, let be $y$ the actual value of the series, $\hat{y}$ the predicted value and $\acute{y}$ the mean of the observed data.

@@

\begin{itemize}
\item 	Patterns: n by m, where n from 1 to 8 and m from 1 to 2.

\item Methods: support vector regression with the kernels functions: linear, RBF (Gaussian) and sigmoid; echo state networks; ordinary least squares linear regression, ridge regression and elastic-net regression.
